---
title: resume2
author: Sintayehu Gebretekle
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['./css/custom_resume.css', './css/styles_html.css','resume']
    #css: ['./css/custom_resume.css', './css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(glue)

#source helper functions
source('helper_functions.R')


# get data from xlsx file
# position_data <- readxl::read_excel('resume_data.xlsx',
#                                     sheet = "positions",
#                                     na = c("", "NA", "na"))
# 
# skill_data <- readxl::read_excel('resume_data.xlsx',
#                                  sheet = "skills",
#                                  na = c("", "NA", "na"))

position_data <- read.csv('./data/position_data.csv', stringsAsFactors = F)
skill_data <- read.csv('./data/skill_data.csv', stringsAsFactors = F)
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------

```{r contactinfo}

# Adjust contact info based on document type - html has link while pdf does not
if(params$doctype == "HTML") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Philadelphia, Pennsylvania
    - <i class="fa fa-phone"></i> <a href="tel:+12068024655">(206) 802-4655</a>
    - <i class="fa fa-envelope"></i> santos_stat@yahoo.com
    - <i class="fa fa-globe"></i> [www.myconnect.gsk.com](https://myconnect.gsk.com/sites/modern#)
    - <i class="fa fa-github"></i> [github.com/santos-stat](https://github.com/santos-stat/Data-driven-resume)
    - <i class="fab fa-linkedin-in"></i> [linkedin.com/sintayehu](https://www.linkedin.com/in/sintayehu-gebretekle-7492a727/)
  ')
} 

if(params$doctype == "PDF") {
  glue::glue('
    - <i class="fa fa-map-marked-alt"></i> Philadelphia, Pennsylvania
    - <i class="fa fa-phone"></i> 206.802.4655
    - <i class="fa fa-envelope"></i> santos_stat<!-- breaking hyplerlink -->@yahoo.com
    - <i class="fa fa-globe"></i> gsk.com
    - <i class="fa fa-github"></i> https://github.com/santos-stat/Data-driven-resume
    - <i class="fab fa-linkedin-in"></i> linkedin.com/sintayehu
  ')
}

```



```{r download}
# if doctype is html add link to download a pdf version
if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download Docx](https://github.com/santos-stat/Data-driven-resume/raw/main/resume2.docx)")
}

```

<br>


Software skills {#skills}
--------------------------------------------------------------------------------

```{r codingskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Tech")

```

R skills {#rpackages}
--------------------------------------------------------------------------------

```{r rskills, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "R Packages")

```

Certifications  {#interests}
--------------------------------------------------------------------------------

```{r learningfocus, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "Interests")

```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------


```{r}

# set disclaimer in bottom right corner based on doctype
if(params$doctype == "HTML") {
  glue::glue("
    Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
    Source code: [**Github repo**](https://github.com/santos-stat/Data-driven-resume).
  ")
} 
if(params$doctype == "PDF") {
  glue::glue("
    Made w/ **pagedown::html_resume**
    Code: **github.com/santos-stat/Data-driven-resume** 
  ")
}
```


Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Sintayehu Gebretekle {#title}
--------------------------------------------------------------------------------
<br>

### Data Scientist  |  Clinical SAS Programmer  |  R Enthusiast

<br>

SAS Certified Base Programmer for SAS 9 and SAS Certified Advanced Programmer for SAS 9 with 10+ years of experience and master’s degree in Biostatistics.<br><br>
Experience as a Clinical SAS Programmer in Pharma/CROs and extensively involved in programming of ADAM Datasets, Tables, Listings and Graphs.<br><br>
Maintained QC checklist, Data Issue log, Analysis Dataset Specification document, Programming Plan, QC Plan documents specific for each study.<br><br>
Excellent experience in SAS/BASE, SAS/MACRO, SAS/STAT, SAS/GRAPH, SAS/ODS, SAS/ENTERPRISE GUIDE and SAS/SQL in Windows and UNIX platforms.<br><br>
Experience in RStudio in producing Excel, RTF, HTML and PDF formatted files and qc’ing ADAM datasets using RStudio.<br><br>
Experience in handling multiple tasks independently in a dynamic and good experience working in a team comprised of various professions.

<br>

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'work')
```

<br>


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```
